Supplemental Material: Multidimensional analysis and detection of informative features in human brain white matter

### 2021-02-02 reports/manuscript/supplemental.tex
Update environment.yml and Dockerfile. Add line numbers to paper

%% ****** Start of file apstemplate.tex ****** %
%%
%%   This file is part of the APS files in the REVTeX 4 distribution.
%%   Version 4.1r of REVTeX, August 2010
%%
%%
%%   Copyright (c) 2001, 2009, 2010 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.0
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showpacs' option to make PACS codes appear
%  Add 'showkeys' option to make keywords appear
\documentclass[10pt,%
               aps,%
               prl,%
               reprint,%
               superscriptaddress,%
               preprintnumbers,%
               amsmath,%
               floatfix]{revtex4-2}
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
\usepackage[export]{adjustbox}  % Used to adjust figure frames
\usepackage{subcaption}
\usepackage{url}
\usepackage{color}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{float}
\usepackage{amsfonts}
\usepackage{wrapfig}
\usepackage{physics}
\usepackage{mathtools}  % For shortintertext
\usepackage[inline]{enumitem}
\usepackage[per-mode=symbol,group-separator={,},group-minimum-digits=4]{siunitx}
\usepackage{todonotes}
\usepackage{graphicx}
\graphicspath{ {../paper_figures} }
\usepackage{bibentry}

@@

Here, we propose that in addition to regularizing the coefficients in
$\hat{\beta}$, we can also capitalize on our knowledge of the group structure
of the bundle profile features in $\mathbf{X}$. The bundle-metric
combinations form a natural grouping. For example, we expect that MD features
within the left arcuate fasciculus will co-vary across individuals. Likewise
for FA values within the right corticospinal tract (CST) and so on. This
group structure is represented in \cref{main:fig:methods:group-structure}, which
depicts the linear model $\hat{y} = \mathbf{X} \hat{\beta}$. Thus, we seek a
regularization approach that will fit a linear model with
anatomically-grouped covariates, where we expect to observe both groupwise
sparsity, where the number of groups (bundle/metric combinations) with at
least one non-zero coefficients is small, as well as within-group sparsity,
where the number of non-zero coefficients within each non-zero group is
small. The sparse group lasso (SGL) is a penalized regression technique that
satisfies these criteria\cite{simon2013sparse}. It solves for a
coefficient vector $\hat{\beta}$ that satisfies
\begin{multline}
    \hat{\beta} = \min_\beta L_{\text{mse}}
    + \left( 1 - \alpha \right) \lambda \displaystyle \sum_{\ell = 1}^{G}
    \sqrt{p_\ell} \norm{\beta^{(\ell)}}_2
    + \alpha \lambda \norm{\beta}_1,\\%
    \text{where} \quad
    L_{\text{mse}} = \frac{1}{2}
    \norm{y - \displaystyle \sum_{\ell = 1}^{G}
    \mathbf{X}^{(\ell)} \beta^{(\ell)}}_2^2.
    \label{eq:sgl}
\end{multline}
Here, $G$ is the number of groups, $\mathbf{X}^{(\ell)}$ is the submatrix of
$\mathbf{X}$ corresponding to group $\ell$, $\beta^{(\ell)}$ is the
coefficient vector for group $\ell$ and $p_\ell$ is the length of
$\beta^{(\ell)}$. In the tractomtetry setting, $G = T \times M$ and $\forall
\ell: p_\ell = 100$. The first term is the mean square error loss,
$L_{\text{mse}}$, as in the standard linear regression framework. The second
and third terms encourage groupwise sparsity and overall sparsity,
respectively. If $\alpha = 1$ the SGL reduces to the traditional
lasso\cite{tibshirani1996regression}. Conversely, if $\alpha = 0$ the SGL
reduces to the group lasso\cite{yuan2006model}. Thus, the model
hyperparameter $\alpha$ controls the combination of group-lasso and lasso.
The hyperparameter $\lambda$ controls the strength of the regularization.

>>>>

%% ****** Start of file apstemplate.tex ****** %
%%
%%   This file is part of the APS files in the REVTeX 4 distribution.
%%   Version 4.1r of REVTeX, August 2010
%%
%%
%%   Copyright (c) 2001, 2009, 2010 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.0
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showpacs' option to make PACS codes appear
%  Add 'showkeys' option to make keywords appear
\documentclass[10pt,%
               aps,%
               prl,%
               reprint,%
               superscriptaddress,%
               preprintnumbers,%
               linenumbers,%
               amsmath,%
               floatfix]{revtex4-2}
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
\usepackage[export]{adjustbox}  % Used to adjust figure frames
\usepackage{subcaption}
\usepackage{url}
\usepackage{color}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{float}
\usepackage{amsfonts}
\usepackage{wrapfig}
\usepackage{physics}
\usepackage{mathtools}  % For shortintertext
\usepackage[inline]{enumitem}
\usepackage[per-mode=symbol,group-separator={,},group-minimum-digits=4]{siunitx}
\usepackage{todonotes}
\usepackage{graphicx}
\graphicspath{ {../paper_figures} }
\usepackage{bibentry}

@@

We propose that in addition to regularizing the coefficients in
$\hat{\beta}$, we can also capitalize on our knowledge of the group structure
of the bundle profile features in $\mathbf{X}$. The bundle-metric
combinations form a natural grouping. For example, we expect that MD features
within the left arcuate fasciculus will co-vary across individuals. Likewise
for FA values within the right corticospinal tract (CST) and so on. This
group structure is represented in \cref{main:fig:methods:group-structure}, which
depicts the linear model $\hat{y} = \mathbf{X} \hat{\beta}$. Thus, we seek a
regularization approach that will fit a linear model with
anatomically-grouped covariates, where we expect to observe both groupwise
sparsity, where the number of groups (bundle/metric combinations) with at
least one non-zero coefficients is small, as well as within-group sparsity,
where the number of non-zero coefficients within each non-zero group is
small. The sparse group lasso (SGL) is a penalized regression technique that
satisfies these criteria\cite{simon2013sparse}. It solves for a
coefficient vector $\hat{\beta}$ that satisfies
\begin{multline}
    \hat{\beta} = \min_\beta L_{\text{mse}}
    + \left( 1 - \alpha \right) \lambda \displaystyle \sum_{\ell = 1}^{G}
    \sqrt{p_\ell} \norm{\beta^{(\ell)}}_2
    + \alpha \lambda \norm{\beta}_1,\\%
    \text{where} \quad
    L_{\text{mse}} = \frac{1}{2}
    \norm{y - \displaystyle \sum_{\ell = 1}^{G}
    \mathbf{X}^{(\ell)} \beta^{(\ell)}}_2^2.
    \label{eq:sgl}
\end{multline}
Here, $G$ is the number of groups, $\mathbf{X}^{(\ell)}$ is the submatrix of
$\mathbf{X}$ corresponding to group $\ell$, $\beta^{(\ell)}$ is the
coefficient vector for group $\ell$ and $p_\ell$ is the length of
$\beta^{(\ell)}$. In the tractomtetry setting, $G = T \times M$ and $\forall
\ell: p_\ell = 100$. The first term is the mean square error loss,
$L_{\text{mse}}$, as in the standard linear regression framework. The second
and third terms encourage groupwise sparsity and overall sparsity,
respectively. If $\alpha = 1$ the SGL reduces to the traditional
lasso\cite{tibshirani1996regression}. Conversely, if $\alpha = 0$ the SGL
reduces to the group lasso\cite{yuan2006model}. Thus, the model
hyperparameter $\alpha$ controls the combination of group-lasso and lasso.
The hyperparameter $\lambda$ controls the strength of the regularization.
